Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-06-14 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
added an axiom to Example 5

\begin{example}\label{exp:dllite}
Given a DL-Lite ontology $\mathcal{O}_{\text{ex}_5}$
where the TBox and RBox contain the following axioms:
$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
its ABox contains an assertion $Q(a,b)$.
We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_5}$ by $P_{\text{ex}_5}=\langle R, \textbf{I}\rangle$,
where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
as the only fact.
The unique materialization graph of $P_{\text{ex}_5}$ is denoted by
$\mathcal{G}_{\text{ex}_5}$ (see
Figure~\ref{fig:ex2}). \textcolor{red}{How is $A(a)$ derived from the
  ontology and $Q(a, b)$?}
\end{example}

>>>>

\begin{example}\label{exp:dllite}
Given a DL-Lite ontology $\mathcal{O}_{\text{ex}_5}$
where the TBox and RBox contain the following axioms:
$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $\exists Q.\top\sqsubseteq A$ and $S\sqsubseteq R$;
its ABox contains an assertion $Q(a,b)$.
We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_5}$ by $P_{\text{ex}_5}=\langle R, \textbf{I}\rangle$,
where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
as the only fact.
The unique materialization graph of $P_{\text{ex}_5}$ is denoted by
$\mathcal{G}_{\text{ex}_5}$ (see
Figure~\ref{fig:ex2}). \textcolor{red}{How is $A(a)$ derived from the
  ontology and $Q(a, b)$?}
\end{example}
